Near Optimal Behavior with Approximate State Abstraction

### 2016-02-03 paper/background.tex
Updated taxi figure for 200 trials

%MDP/SDM Background and Notation
\subsection{\acp{MDP} and Sequential Decision Making}
An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards. We assume without loss of generality that all reward functions are normalized to $[0,1]$.

>>>>

%MDP/SDM Background and Notation
\subsection{\acp{MDP} and Sequential Decision Making}
\enote{Come back to this and make sure it covers everything that needs to be covered and matches all our notation.}
An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent transitioning to state $s' \in \mathcal{S}$ after applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards. We assume without loss of generality that all reward functions are normalized to $[0,1]$.

### 2016-02-03 paper/results_discussion.tex
Updated taxi figure for 200 trials

%Explanation of what plots done
For each domain we report two quantities as a function of epsilon. First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}. The smaller this value, the smaller the state space of the $\ac{MDP}$ that the agent must plan over. Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2}. 200 Trials are run for each data point.

@@

% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For Taxi and Random.
\begin{figure}
\label{fig:main_empirical_results2}
\centering
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}
}

>>>>

%Explanation of what plots done
For each domain we report two quantities as a function of epsilon with \%95 confidence bars. First, we compare the number of states in the abstract \ac{MDP} to different values of $\epsilon$, shown in Figure~\ref{fig:main_empirical_results1}. The smaller this value, the smaller the state space of the $\ac{MDP}$ that the agent must plan over. Second, we report the value under the abstract policy of the initial ground state, shown in Figure~\ref{fig:main_empirical_results2}. 200 Trials are run for each data point.

@@

% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For Taxi and Random.
\begin{figure}
\label{fig:main_empirical_results2}
\centering
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.pdf}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
